The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-03-30 albatros_paper.tex
HCC: starting to edit intro text

\title{Instructions for Typesetting Manuscript\\
Using \LaTeX\footnote{For the title, try not to use more than
three lines. Typeset the title in 11 pt Times Roman,
boldface, with the first letter of important words capitalized.}}

@@

\section{Introduction}
\noindent The \SI{21}{\cm} wavelength of hydrogen gas is being observed by several experiments which are modelled for the purpose of Hydrogen mapping in our Universe. This hydrogen line is a significant mechanism as it helps in the probing of the dark ages to the epoch of reionization (EoR) \cite{2013PhRvD..87d3002L,2014ApJ...782...66P}.\\

>>>>

\title{The Array of Long-Baseline Antennas for Taking Radio
  Observations from the Sub-Antarctic}

@@

\section{Introduction}

Measurements of redshifted \SI{21}{\cm} emission of neutral hydrogen
across a wide range of radio frequencies have the potential to
elucidate the universe's history from the cosmic ``dark ages'' up to
the formation of large-scale structures (see,
e.g.,~\citep{ska_physics,2013PhRvD..87d3002L,2014ApJ...782...66P}.
The dark ages, which occurred after recombination and correspond to a
period when the universe was filled with neutral hydrogen, are
unexplored to date and represent one of the final observational
frontiers in cosmology.  This epoch contains a potential wealth of
cosmological information~\citep{loeb_zaldarriaga}, but the required
redshifted frequencies of $\lesssim 30$~MHz are exceptionally
difficult to observe.  The primary challenges include Galactic
foreground emission, ionospheric interference, and terrestrial
radio-frequency interference (RFI). \\

% At the very lowest frequencies, the state of the art among
% ground-based measurements dates from the 1950s, when Reber and Ellis
% caught brief glimpses of the $\sim 2$~MHz sky at low
% resolution~\citep{reber}.  The lowest frequency to date for
% high-resolution sky imaging has been achieved by the LWA, which
% reported observations at 36.5~MHz using only 28 hours of
% data~\citep{lwa}.  Preliminary observations from Marion Island
% (\S\ref{s:dark_method}) suggest that despite the present-day RFI
% environment, low-frequency observations may still be accessible from
% carefully selected locations and with new technology developments.
